---
title: "methylTFRAnnotationMm10"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{methylTFRAnnotationMm10}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# Overview

`methylTFRAnnotationMm10` provides the genome annotations `methylTFR` needs to
compute bias-corrected transcription factor deviation scores on Mm10:

- **binding sites**, one `GRanges` per motif, each range extended
  so that methylation can be read across the footprint window;
- **motif GC frequency tables**, recording how each motif's binding
  sites distribute across genome-wide GC quintiles;
- **the genome-wide GC distribution**, which assigns each
  methylation call to a GC bin.

The GC tables are what make the deviation score bias-corrected. A
motif whose binding sites sit in GC-rich sequence will overlap CpG
islands more often than one that does not, and CpG islands are
hypomethylated; without the correction that difference in sequence
composition would read as a difference in factor activity.

The data are too large to ship inside the package, so they are
hosted on AnnotationHub and downloaded on first use. Subsequent
calls are served from the local AnnotationHub cache.

# Usage

```{r, eval = FALSE}
library(methylTFRAnnotationMm10)

tf_bindsites <- getTFbindsites("altius")
gcfreqs      <- getGCfreq("altius")
gc_dist      <- getGenomeGC()
```

These are passed straight to `methylTFR::run_methyltfr()`.

# Available motif sets

```{r, eval = FALSE}
methylTFRAnnotationMm10:::.MOTIF_SETS
```

# Session info

```{r}
sessionInfo()
```
